Concurrent Programming in Harmony

### 2021-01-22 book/paper.tex
Latest and greatest
Latest

Method \texttt{incrementer} takes a parameter called \textit{self}.
It increments \textit{count} and sets \textit{done}[\textit{self}] to \texttt{True}.
It then waits until the other thread is done.
(\textbf{await} $c$ is semantically the same as \textbf{while not} $c$: \textbf{pass}.)
After that, method \texttt{incrementer}
verifies that the value of \textit{count} equals 2.
Like Python, Harmony supports \texttt{assert} statements with two arguments:
the first is a Boolean condition, and the second is a value that is
reported if the condition fails, in this case
the value of \textit{count}.

@@

Next to the status, the table shows the \emph{stack trace} of the
thread.  A stack trace is a list of methods that are being invoked.
In this case, the \texttt{implementer} method does not invoke any
other methods, and so the list is of length 1.
For each entry in the stack trace, it shows the method name and
arguments, as well as the variables of the method.

@@

\begin{figure}
\includegraphics[width=\textwidth]{figures/naiveLock.png}
\caption{The \harmonyref{naiveLock.html}{HTML output of running Harmony on \autoref{fig:uplock}}.}
\label{fig:naiveLockhtml}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\textwidth]{figures/naiveFlags.png}
\caption{The \harmonyref{naiveFlags.html}{HTML output of running Harmony on \autoref{fig:upflags}}.}
\label{fig:naiveflagshtml}
\end{figure}

>>>>

Method \texttt{incrementer} takes a parameter called \textit{self}.
It increments \textit{count} and sets \textit{done}[\textit{self}] to \texttt{True}.
It then waits until the other thread is done.
(\textbf{await} $c$ is semantically the same as \textbf{while not} $c$: \textbf{pass}.)
After that, method \texttt{incrementer}
verifies that the value of \textit{count} equals 2.
% Like Python, Harmony supports \texttt{assert} statements with two arguments:
% the first is a Boolean condition, and the second is a value that is
% reported if the condition fails, in this case
% the value of \textit{count}.

@@

The stack of each thread is subdivided into two parts: the
\emph{stack trace} and the \emph{stack top}.
A stack trace is a list of methods that are being invoked.
In this case, the \texttt{implementer} method does not invoke any
other methods, and so the list is of length 1.
For each entry in the stack trace, it shows the method name and
arguments, as well as the variables of the method.
The stack top shows the values on the stack beyond the stack trace.

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.8\textwidth]{figures/naiveLock.pdf}
\end{center}
\caption{The \harmonyref{naiveLock.html}{HTML output of running Harmony on \autoref{fig:uplock}}.}
\label{fig:naiveLockhtml}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.8\textwidth]{figures/naiveFlags.pdf}
\end{center}
\caption{The \harmonyref{naiveFlags.html}{HTML output of running Harmony on \autoref{fig:upflags}}.}
\label{fig:naiveflagshtml}
\end{figure}
